---
title: "statsProject"
Names: Andre Mojica, Nadezhda Dominguez Salinas, Yeshe Jangchup, Ramatoulaye Bah
output: html_document
---

Libraries:

```{r}
library(tidyverse)
library(ggplot2)
```

```{r}
#The runtime of the shows listed is in minutes and represents how long on average ONE episode of the show is/how long the movie is.

movieTitles <- read_csv("titles.csv") %>% 
  rename(show_title = title) %>% 
  mutate(seasons = ifelse(is.na(seasons), 0, seasons)) %>% 
  select(-type, -description, -age_certification, -imdb_id, -id) 

globalViewership <- read_csv("all-weeks-global.csv") %>% 
  select(-season_title, -runtime, -weekly_views, -episode_launch_details, -weekly_rank, -is_staggered_launch) %>% 
  mutate(week = as.character(week)) %>% 
  filter(grepl('2022', week)) %>% 
  group_by(show_title, category) %>% 
  summarise(weekly_hours_viewed = sum(weekly_hours_viewed), 
            cumulative_top10 = sum(cumulative_weeks_in_top_10)) %>% 
  mutate(weekly_hours_viewed = weekly_hours_viewed/10000)

cleaned_data <- globalViewership %>% 
  inner_join(movieTitles, by = "show_title")
 

cleaned_data <- cleaned_data %>%
  mutate(genre1=gsub(",.*","]",genres), 
         filteredproduction_countries=gsub(",.*","]",production_countries)) %>% 
  select(-genres, -production_countries) %>%
  filter(cumulative_top10 < 100)

# Introduction (Table 1)
summary(cleaned_data)
```

**Explanations of the variables in the summary:**

>


**Visualizations: **

```{r}
model1 <- lm(weekly_hours_viewed ~ runtime + category + cumulative_top10 + genre1, cleaned_data)
summary(model1)

coef(model1)

model2 <- lm(weekly_hours_viewed ~ cumulative_top10 + filteredproduction_countries, cleaned_data)
summary(model2)
```


# Weekly Hour vs. Cumulative_Top 10
```{r}
ggplot(cleaned_data, aes(x = cumulative_top10, y = weekly_hours_viewed, color = category)) +
  geom_point() + 
  theme_bw()
  
```

```{r}
ggplot(cleaned_data, aes(x = runtime, category)) +
  geom_boxplot() +
  theme_bw()
```

```{r}
ggplot(cleaned_data, aes(x = tmdb_popularity, weekly_hours_viewed, color = genre1)) +
  geom_point() +
  geom_smooth(se = FALSE)
  theme_bw()
```

```{r}
ggplot(cleaned_data, aes(x = genre1)) +
  geom_bar()
```
the shows that usually end up ion the top 10 are biased towards shows and films that are under the drama category.


**Our Structure for the project paper:**

What do the visualization predict?

Explain what our research question is

The methodology behind our research question

If effect modifiers/confounding variables are taken into account and how we will assess it, (hypothesis testing, p value), and why?
